### 2022-01-28 input/conclusion.tex
few fixes in conclusions

At mid-term, we plan to evaluate our proposal within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem
(IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
relevance of the \NAME approach in a real system subject to high
dynamicity, and compare it against its current DHT-based indexing
system that does not include distance in its operation. More generally,
we claim \NAME (or \NAMEC) can constitute a novel building block for
geo-distributed services.  Among the use-cases we have identified,
\NAME can be used to complement content delivery infrastructures by
efficiently sharing between \process attached to the same CDN server
the locatiosn of web objects that have been already downloaded. This
would allow the containment of web traffic even lower in our networks,
and so reduce the overall traffic footprint.

>>>>

At mid-term, we plan to evaluate our proposal within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem
(IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
relevance of the \NAME approach in a real system subject to high
dynamicity, and compare it against its current DHT-based indexing
system that does not include distance in its operation. More
generally, we claim that \NAME (or \NAMEC) can constitute a novel
building block for geo-distributed services.  For instance, \NAME
could complement content delivery infrastructures by efficiently
sharing between \processes attached to the same CDN server the
locations of web objects that have already been downloaded. This would
further improve the containment of web traffic in our networks, and in
turns, reduce the overall traffic footprint.
